Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2023-12-11 manuscript/manuscript.Rmd

Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza (e.g. \cite{mcgowanCollaborativeEffortsForecast2019, reichCollaborativeMultiyearMultimodel2019,  shamanForecastingSeasonalOutbreaks2012, biggerstaffResultsCentersDisease2016}), dengue fever [e.g. @johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g. @viboudRAPIDDEbolaForecasting2018; @funkAssessingPerformanceRealtime2019], chikungunya [e.g. @delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g. @funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021]. Applications of epidemiological models differ in the way they make statements about the future. Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past. Forecasts can be judged by comparing them against observed data. Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.

>>>>

\cite{mcgowanCollaborativeEffortsForecast2019}

Infectious disease modelling has a long tradition and has helped inform public health decisions both through scenario modelling, as well as actual forecasts of (among others) influenza [e.g. @mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g. @johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g. @viboudRAPIDDEbolaForecasting2018; @funkAssessingPerformanceRealtime2019], chikungunya [e.g. @delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g. @funkShorttermForecastsInform2020; @cramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @bracherNationalSubnationalShortterm2021; @europeancovid-19forecasthubEuropeanCovid19Forecast2021]. Applications of epidemiological models differ in the way they make statements about the future. Forecasts aim to predict the future as it will occur, while scenario modelling and projections aim to represent what the future could look like under certain scenario assumptions or if conditions stayed the same as they were in the past. Forecasts can be judged by comparing them against observed data. Since it is much harder to fairly assess the accuracy and usefulness of projections and scenario modelling in the same way, this work focuses on forecasts, which represent only a subset of all epidemiological modelling.
